\vspace{-1cm}
\renewcommand{\refname}{}

\renewcommand\bibpreamble{$\rightarrow$ The references to go further or deeper for advanced readers are prepended by an asterisk.\bigskip}

\begin{thebibliography}{99}
		
	\bibitem[Berrou et al., sept 2012]{bg3}
	 * Claude Berrou, Vincent Gripon. \textit{Nearly-optimal associative memories based on distributed constant weight codes}. Information Theory and Applications Workshop, September 2012, pp. 269 to 273.\\ \href{https://www.researchgate.net/publication/254026422\_Nearly-optimal\_associative\_memories\_based\_on\_distributed\_constant\_weight\_codes}{\scriptsize{\texttt{https://www.researchgate.net/publication/254026422}}} \normalsize{}
	
	\bibitem[Berrou et al., 2012]{bg1} 
	Claude Berrou, Vincent Gripon. \textit{Petite mathématique du cerveau -- Une théorie de l’information mentale}. Odile Jacob, 2012.
	
	\bibitem[Berrou et al., 2011]{bg2}
	 * Claude Berrou, Vincent Gripon. \textit{Sparse Neural Networks With Large Learning Diversity}. IEEE transactions on neural networks, Volume 22, 2011, pp. 1087 to 1096.\\ \href{https://arxiv.org/pdf/1102.4240}{\scriptsize{\texttt{https://arxiv.org/pdf/1102.4240}}} \normalsize{}
	 	 
	 \bibitem[Klein, 2020]{cse}
	 CentraleSupélec. \textit{Cours d'Etienne Klein : les deux théories de la relativité d'Albert Einstein}. 
	 YouTube, 23 avril 2020. \\ \href{https://www.youtube.com/watch?v=1NQ6WHDgtM0}{\scriptsize{\texttt{https://www.youtube.com/watch?v=1NQ6WHDgtM0}}} \normalsize{}
	 
	 \bibitem[Chavent, 2013]{mc}
	 Marie Chavent. \textit{La classification automatique de données quantitatives}. 
	 Institut de Mathématiques de Bordeaux UMR 5251, 2013.\\ \href{http://www.math.u-bordeaux.fr/\~mchave100p/wordpress/wp-content/uploads/2013/10/cours\_classif\_quanti.pdf}{\scriptsize{\texttt{http://www.math.u-bordeaux.fr/$\sim$mchave100p/.../2013/10/cours\_classif\_quanti.pdf}}} \normalsize{}
	 
	 \bibitem[Demoures et al., 2005]{fxd}
	 François-Xavier Demoures, Eric Monnet. \textit{Le monde à l’épreuve de l’imagination. Sur << l’expérimentation mentale >>}. Tracés, 2005 \\ \href{https://journals.openedition.org/traces/177}{\scriptsize{\texttt{https://journals.openedition.org/traces/177}}} \normalsize{}
	 
	 \bibitem[Georgeon et al., 2011]{ger}
	 Olivier Georgeon, Frank Ritter. \textit{An intrinsically-motivated schema mechanism to model and simulate emergent cognition}. 
	 Cognitive Systems Research, 2011. {\scriptsize [ doi:10.1016/j.cogsys.2011.07.003 ]}
	 \\ \href{https://projet.liris.cnrs.fr/ideal/doc/GeorgeonO2011-emergent-cognition.pdf}{\scriptsize{\texttt{https://projet.liris.cnrs.fr/ideal/doc/GeorgeonO2011-emergent-cognition.pdf}}} \normalsize{}
	 
	 \bibitem[Goldberg, 2001]{re}
	 * David Goldberg. \textit{What Every Computer Scientist Should Know About Floating-Point Arithmetic}. Numerical Computation Guide, July 2001, pp. 171 to 264.\\ \href{https://ece.uwaterloo.ca/\~dwharder/NumericalAnalysis/02Numerics/Double/paper.pdf}{\scriptsize{\texttt{https://ece.uwaterloo.ca/$\sim$dwharder/NumericalAnalysis/02Numerics/Double/paper.pdf}}} \normalsize{}
	 
	 \bibitem[Ics, 2014/20]{yi}
	 Yann Ics. \textit{Journal of Generative Sonic Art}. Web publication, 2014/2020.\\ \href{https://www.overleaf.com/read/sjhfhthgkgdj}{\scriptsize{\texttt{https://www.overleaf.com/read/sjhfhthgkgdj}}} \normalsize{}
	
	 \bibitem[Jiang et al., 2012]{bg4}
	 * Xiaoran Jiang, Vincent Gripon, Claude Berrou. \textit{Learning long sequences in binary neural networks}. 4th International Conference on Advanced Cognitive Technologies and Applications, July 2012, pp. 165 to 170.\\ \href{https://www.researchgate.net/profile/Xiaoran\_Jiang/publication/265508848\_Learning\_Long\_Sequences\_in\_Binary\_Neural\_Networks/links/54107a6c0cf2f2b29a410d8c.pdf}{\scriptsize{\texttt{https://www.researchgate.net/profile/Xiaoran\_Jiang/publication/265508848}}} \normalsize{}
	 
	 \bibitem[McLuhan, 1964]{mm} 
	Marshall McLuhan. \textit{Understanding Media -- The Extensions of  Man}. First edition 1964, MIT Press edition, 1994.
				 
	 \bibitem[Shalizi, 2009]{cs}
	 Cosma Shalizi. \textit{Distances between Clustering, Hierarchical Clustering}. 
	 36-350, Data Mining, 2009.\\ \href{http://www.stat.cmu.edu/\~cshalizi/350/lectures/08/lecture-08.pdf}{\scriptsize{\texttt{http://www.stat.cmu.edu/$\sim$cshalizi/350/lectures/08/lecture-08.pdf}}} \normalsize{}
	 
	  \bibitem[Wells, 1896]{hgw} 
	Herbert-George Wells. \textit{L'Ile du docteur Moreau}. First edition 1896 [\textit{The Island of Dr. Moreau}], Club fran\c{c}ais du livre, Paris 1961. Traduction Henry Durand-Davray. 
		 
\end{thebibliography}